Identifying Heterogeneity in SAR Data with New Test Statistics

### 2024-11-24 Text/2024PresentationsChina.tex
Update 2024PresentationsChina.tex

Now, given the random sample $\bm Z=(Z_1,Z_2,\dots,Z_n)$ and its sorted version $Z_{(1)},Z_{(2)},\dots,Z_{(n)}$, we can 
\begin{itemize}
	\item estimate $F$ by the empirical cumulative distribution function,
	\item its inverse, the quantile function $F^{-1}$, by the order statistics
	\item approximate the derivative with finite differences (called ``spacings''),
	\item approximate the integral with a summation.
\end{itemize}

There are several versions of entropy estimators based on spacings.
We found that the best in terms of bias and mean square error is the one proposed by
\citet{IbrahimAlOmari2014}:
 \[
	\widehat{H}_{\text{AO}}(\bm{Z})=\frac{1}{n} \sum_{i=1}^n \log \left[\frac{n}{\omega_i m}\left(Z_{(i+m)}-Z_{(i-m)}\right)\right],
	\] where \[
	\omega_i= \begin{cases}3/2 & \text { if }\quad 1 \leq i \leq m, \\ 2 & \text { if }\quad m+1 \leq i \leq n-m, \\ 3/2 & \text { if } \quad n-m+1 \leq i \leq n,\end{cases}
	\] 
	in which \(m=\big[\sqrt{n}+0.5\big]\), \(Z_{(i-m)}=Z_{(1)}\) for \(i \leq m\), and
	\(Z_{(i+m)}=Z_{(n)}\) for \(i \geq n-m\).

>>>>

Now, given the random sample $\bm Z=(Z_1,Z_2,\dots,Z_n)$ and its sorted version $Z_{(1)},Z_{(2)},\dots,Z_{(n)}$, we can 
\begin{itemize}
	\item estimate $F$ by the empirical cumulative distribution function,
	\item its inverse, the quantile function $F^{-1}$, by the \alert{order statistics}
	\item approximate the derivative with finite differences (called \alert{``spacings''}),
	\item approximate the integral with a \alert{summation}.
\end{itemize}

\citet{vasicek1976test} proposed estimators based on spacings ($m$), followed by several other versions.
We found that the best in terms of bias and mean square error is the one proposed by
\citet{IbrahimAlOmari2014}:
 \[
	\widehat{H}_{\text{AO}}(\bm{Z})=\frac{1}{n} \sum_{i=1}^n \log \left[\frac{n}{\omega_i m}\left(Z_{(i+m)}-Z_{(i-m)}\right)\right],
	\] where \[
	\omega_i= \begin{cases}3/2 & \text { if }\quad 1 \leq i \leq m, \\ 2 & \text { if }\quad m+1 \leq i \leq n-m, \\ 3/2 & \text { if } \quad n-m+1 \leq i \leq n,\end{cases}
	\] 
	in which \(m=\big[\sqrt{n}+0.5\big]\), \(Z_{(i-m)}=Z_{(1)}\) for \(i \leq m\), and
	\(Z_{(i+m)}=Z_{(n)}\) for \(i \geq n-m\).
